|

### 2023-03-10 paper.Rmd

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown^[Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  | Download: https://osf.io/q395s
  |
  | Feedback? Errors? mail@paulcbauer.eu
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
  |
  | Tired of Latex?
  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

# Prerequesites
I assume that you are using R on a day-to-day basis. You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown. If you don't know what R Markdown is watch [this short video](https://vimeo.com/178485416). Then...

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 5 input files I created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). Ignore the other files.

@@

* ...a `paper.rmd` file (the underlying R Markdown file).
* ...a `references.bib` file (the bibliography).
    + I use paperpile to manage my references and export the `.bib` file into the folder that contains my `.rmd` file.
* ...a `data.csv` file (some raw data).
* ... a `american-sociological-association.csl` file that defines the style of your bibliography.^[You can download various citation style files from this webpage: https://github.com/citation-style-language/styles.]

@@

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in Section \@ref(sec:tables) you can find different ways of referencing tables. The code of the underlying `paper.rmd` will show you how I referenced Section \@ref(sec:tables) right here namely with '`Section \@ref(sec:tables)`'.

@@

I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \@ref(sec:rsessioninfo). This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see [packrat](https://rstudio.github.io/packrat/).

@@

Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).

@@

# Good practices
Every researcher has his own optimized setup. Currently I would recommend the following:

>>>>

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown^[Corresponding address: mail@paulcbauer.de. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author:
  - Paul Bauer, Mannheim Centre for European Social Research
  - Camille Landesvatter, Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  | Download: https://osf.io/q395s
  |
  | Feedback? Errors? mail@paulcbauer.eu
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
  |
  | Tired of Latex?
  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

# Prerequesites
We assume that you are using R on a day-to-day basis. You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown. If you don't know what R Markdown is watch [this short video](https://vimeo.com/178485416). Then...

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 5 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). Ignore the other files.

@@

* ...a `paper.rmd` file (the underlying R Markdown file).
* ...a `references.bib` file (the bibliography).
    + We use paperpile to manage my references and export the `.bib` file into the folder that contains my `.rmd` file.
* ...a `data.csv` file (some raw data).
* ... a `american-sociological-association.csl` file that defines the style of your bibliography.^[You can download various citation style files from this webpage: https://github.com/citation-style-language/styles.]

@@

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in Section \@ref(sec:tables) you can find different ways of referencing tables. The code of the underlying `paper.rmd` will show you how we referenced Section \@ref(sec:tables) right here namely with '`Section \@ref(sec:tables)`'.

@@

We would recommend to use the command below and simply add it to the appendix as we did here in Appendix \@ref(sec:rsessioninfo). This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see [packrat](https://rstudio.github.io/packrat/).

@@

Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] We normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).

@@

# Good practices
Every researcher has his own optimized setup. Currently we would recommend the following:
